\vspace{-13mm}\includegraphics[width=15mm,scale=3]{../images/IST_Logo.png} \\ {\fontsize{24}{16}Detection of Li in Technological Materials through Nuclear Reactions} \vspace{-5mm}

### 2024-01-20 text/paper/paper.tex
Saturday, 20 January 2024 at 18:04:11
paper.tex

%\begin{center}
%    \label{TT_21}
%    \centering
%    \includegraphics[scale = 0.6]{images/TT_21_Chn1.png}
%    \captionof{figure}{Channel 1 spectrum fit with [\ref{eq:califit}]}
%\end{center}
%
%\begin{center}
%    \label{TT_21}
%    \centering
%    \includegraphics[scale = 0.6]{images/TT_21_Chn2.png}
%    \captionof{figure}{Channel 2 spectrum fit with [\ref{eq:califit}]}
%\end{center}

@@

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.3]{../../images/Chn0_calib_with_Backscattering.png}
    \captionof{figure}{Calibration "detector 0"}
\end{center}

@@

%\begin{center}
%    \label{TT_21}
%    \centering
%    \includegraphics[scale = 0.6]{images/TT_21_Chn1_calib.png}
%    \captionof{figure}{Calibration Channel 1}
%\end{center}
%
%The calibration equation for channel 1 is:
%
%\begin{equation}
%    \begin{split}
%        E[\text{keV}] &= m_1 \times E[\text{Chn}] + b_1 \\
%        m_1 &= 8.97 \pm 0.03 \\
%        b_1 &= 55.40 \pm 17.53
%    \end{split}
%    \label{eq:calib1}
%\end{equation}
%
%\begin{center}
%    \label{TT_21}
%    \centering
%    \includegraphics[scale = 0.6]{images/TT_21_Chn2_calib.png}
%    \captionof{figure}{Calibration Channel 2}
%\end{center}
%
%The calibration equation for channel 2 is:
%
%\begin{equation}
%    \begin{split}
%        E[\text{keV}] &= m_2 \times E[\text{Chn}] + b_2 \\
%        m_2 &= 9.07 \pm 0.12 \\
%        b_2 &= 48.17 \pm 69.69
%    \end{split}
%    \label{eq:calib2}
%\end{equation}
%

@@

\begin{center}
    \label{alfa_peaks}
    \centering
    \includegraphics[scale = 0.3]{../../images/AlphaPeaks.png}
    \captionof{figure}{Theoretical energy values of the two alphas}
\end{center}

@@

\begin{center}
    \centering
    \includegraphics[scale = 0.3]{../../images/OverlapLiF_NC.png}
    \captionof{figure}{Spectrum of the $\ce{LiF}$ sample}
\end{center}

@@

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.3]{../../images/FullAnalysisLiF.png}
    \captionof{figure}{Full Analysis of $\ce{LiF}$ Spectrum}
\end{center}

@@

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.3]{../../images/OverlapLiAlO2.png}
    \captionof{figure}{Spectrum of the $\ce{LiAlO_2}$ sample}
\end{center}

@@

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.3]{../../images/FullAnalysisLiAlO2.png}
    \captionof{figure}{Full Analysis of $\ce{LiAlO_2}$ Spectrum}
\end{center}

@@

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.3]{../../images/OverlapImplanted.png}
    \captionof{figure}{Spectrum of the implanted sample}
\end{center}

@@

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.3]{../../images/FullAnalysisImplanted.png}
    \captionof{figure}{Full Analysis of the Implanted Sample Spectrum}
\end{center}

@@

To sum up, we were able to successfully conduct the proposed research project.
Nuclear reactions is a very effective technique to detect the presence of elements in samples, although its cost is high.
We were able to detect the presence of lithium in all the samples. 
Furthermore, we managed to go beyond our proposal and estimate the amount of lithium in each sample.
% The results obtained were in accordance with the values obtained from the Danish Institute that provided the samples. MEIO INVENTADO

>>>>

%\begin{center}
%    \label{TT_21}
%    \centering
%    \includegraphics[scale = 0.6]{images/TT_21_Chn1.jpeg}
%    \captionof{figure}{Channel 1 spectrum fit with [\ref{eq:califit}]}
%\end{center}
%
%\begin{center}
%    \label{TT_21}
%    \centering
%    \includegraphics[scale = 0.6]{images/TT_21_Chn2.jpeg}
%    \captionof{figure}{Channel 2 spectrum fit with [\ref{eq:califit}]}
%\end{center}

@@

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.3]{../../images/Chn0_calib_with_Backscattering.jpeg}
    \captionof{figure}{Calibration "detector 0"}
\end{center}

@@

%\begin{center}
%    \label{TT_21}
%    \centering
%    \includegraphics[scale = 0.6]{images/TT_21_Chn1_calib.jpeg}
%    \captionof{figure}{Calibration Channel 1}
%\end{center}
%
%The calibration equation for channel 1 is:
%
%\begin{equation}
%    \begin{split}
%        E[\text{keV}] &= m_1 \times E[\text{Chn}] + b_1 \\
%        m_1 &= 8.97 \pm 0.03 \\
%        b_1 &= 55.40 \pm 17.53
%    \end{split}
%    \label{eq:calib1}
%\end{equation}
%
%\begin{center}
%    \label{TT_21}
%    \centering
%    \includegraphics[scale = 0.6]{images/TT_21_Chn2_calib.jpeg}
%    \captionof{figure}{Calibration Channel 2}
%\end{center}
%
%The calibration equation for channel 2 is:
%
%\begin{equation}
%    \begin{split}
%        E[\text{keV}] &= m_2 \times E[\text{Chn}] + b_2 \\
%        m_2 &= 9.07 \pm 0.12 \\
%        b_2 &= 48.17 \pm 69.69
%    \end{split}
%    \label{eq:calib2}
%\end{equation}
%

@@

\begin{center}
    \label{alfa_peaks}
    \centering
    \includegraphics[scale = 0.3]{../../images/AlphaPeaks.jpeg}
    \captionof{figure}{Theoretical energy values of the two alphas}
\end{center}

@@

\begin{center}
    \centering
    \includegraphics[scale = 0.3]{../../images/OverlapLiF_NC.jpeg}
    \captionof{figure}{Spectrum of the $\ce{LiF}$ sample}
\end{center}

@@

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.3]{../../images/FullAnalysisLiF.jpeg}
    \captionof{figure}{Full Analysis of $\ce{LiF}$ Spectrum}
\end{center}

@@

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.3]{../../images/OverlapLiAlO2.jpeg}
    \captionof{figure}{Spectrum of the $\ce{LiAlO_2}$ sample}
\end{center}

@@

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.3]{../../images/FullAnalysisLiAlO2.jpeg}
    \captionof{figure}{Full Analysis of $\ce{LiAlO_2}$ Spectrum}
\end{center}

@@

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.3]{../../images/OverlapImplanted.jpeg}
    \captionof{figure}{Spectrum of the implanted sample}
\end{center}

@@

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.3]{../../images/FullAnalysisImplanted.jpeg}
    \captionof{figure}{Full Analysis of the Implanted Sample Spectrum}
\end{center}

@@

To sum up, we were able to successfully conduct the proposed research project.
Nuclear reactions can be a very effective technique to detect the presence of elements in samples, despite its high cost.
We were able to detect the presence of lithium in all the samples. 
Furthermore, we managed to go beyond our proposal and estimate the amount of lithium in each sample.
% The results obtained were in accordance with the values obtained from the Danish Institute that provided the samples. MEIO INVENTADO
